# Introduction

This is a book created from markdown and executable code.

See @knuth84 for additional discussion of literate programming.



# Fig. 1b: Grouped Phylum Barplots

```{r}

```
```{r}
# ====================================================================
# 1. 加载必要的包
# 如果你之前没有安装过 readxl，请先在控制台运行：install.packages("readxl")
library(readxl)  # 专门用于读取 Excel 文件的包
library(ggplot2)
library(dplyr)

# ====================================================================
# 2. 导入数据 (使用 read_excel 读取 .xlsx 文件)
# 注意这里改用 read_excel 了，并且文件名就是你的 xlsx 文件
bb <- read_excel("D:/2026-d2rs/my-website/happy/ren/Fig.1b.xlsx")

# 转换回普通的数据框格式，以防格式冲突
bb <- as.data.frame(bb)

# ====================================================================
# 3. 整理图例顺序 (Phylum)
bb_order <- c(unique(bb %>% filter(Phylum != 'Unknown/Other') %>% pull(Phylum)) %>% sort())

if("Unknown/Other" %in% bb$Phylum) {
  bb_order <- c(bb_order, 'Unknown/Other')
}

bb$Phylum <- factor(bb$Phylum, levels = bb_order)

# ====================================================================
# 4. 开始绘图
p = ggplot(bb, aes(x = Day, y = Abundance, fill = Phylum))+
  geom_bar(stat = "identity", 
           position = "stack", 
           color = "black") +
  theme_classic(base_size = 18) +
  guides(fill = guide_legend(override.aes = list(colour = NULL), reverse=F)) + 
  theme(legend.key = element_rect(colour = "black")) + 
  theme(legend.position = "right",
        legend.text = element_text(size = 16)) + 
  ylab('Rel. Abundance') + 
  facet_wrap('Diet') + 
  xlab('')

# 显示图片
print(p)

# ====================================================================
# 5. 保存图片
ggsave("D:/2026-d2rs/my-website/happy/ren/Fig_1b_Grouped_Phylum_Barplot.png", height = 6, width = 7)